Equations & R Code

### 2017-05-08 manuscript/coexistence-stability_ms.Rmd
adds pdf of fig 1

g_strg <- grid.arrange(strg_uptake_plot, strg_germ_plot, 
                       reln_uptake_plot, reln_germ_plot,
                       ncol=2, nrow=2)

>>>>

g_strg <- grid.arrange(strg_uptake_plot, strg_germ_plot, 
                       reln_uptake_plot, reln_germ_plot,
                       ncol=2, nrow=2)
ggsave("figure1_onthefly.pdf",plot = g_strg, height = 3, width = 5, units = "in",dpi = 300)
